# Statistical Methods for Data Science - Final Project
# Team:
#   Phanindra Pydisetty (PXP180031)
#   Akhil Bitra (AXB170061)

Load required packages
```{r}
library(dplyr)
library(fitdistrplus)
```

LOAD THREE TOKENS BNB, STATUSNETWORK, MCAP
```{r}
bnb <- read.table('iTokens/networkbnbTX.txt', sep = " ")
statusnetwork <- read.table('iTokens/networkstatusnetworkTX.txt', sep = " ")
mcap <- read.table('iTokens/networkmcapTX.txt', sep=" ")

```

NAMING FOUR COLUMNS OF TOKENS
```{r}
colNames <- c('Seller', 'Buyer', 'Time', 'Amount')
names(bnb) <- colNames
names(statusnetwork) <- colNames
names(mcap) <- colNames
```

SUPPLY DECIMALS FROM ETHERSCAN.IO TO FILTER OUTLIERS
```{r}
supply_bnb <- 183345602.24249
supply_statusnetwork <- 6804870174.8781
supply_mcap <- 100000000
decimals_bnb <- 10^18
decimals_statusnetwork <- 10^18
decimals_mcap <- 10^8
```

FILTERED TOKENS AFTER REMOVING OUTLIERS
```{r}
bnbFiltered <- bnb %>% filter((Amount < decimals_bnb * supply_bnb) & Buyer != 0 & Seller != 0)
statusnetworkFiltered <- statusnetwork %>% filter(Amount < decimals_statusnetwork * supply_statusnetwork & Buyer != 0 & Seller != 0)
mcapFiltered <- mcap %>% filter(Amount < decimals_mcap * supply_mcap & Buyer != 0 & Seller != 0)
```

CALCULATING NUMBER OF OUTLIERS, TOTAL ROWS, FILTERED TOKENS
```{r}
nrow(bnb)
nrow(bnbFiltered)
bnb %>% filter(Amount >= decimals_bnb * supply_bnb) %>% nrow()

nrow(statusnetwork)
nrow(statusnetworkFiltered)
statusnetwork %>% filter(Amount >= decimals_statusnetwork * supply_statusnetwork) %>% nrow()

nrow(mcap)
nrow(mcapFiltered)
mcap %>% filter(Amount >= decimals_mcap * supply_mcap) %>% nrow()
```

Conclusion - We dont have outliers more than 30.


GROUPING BUYER-SELLER PAIRS
We are swapping values of buyer and seller and grouping them.

```{r}
# BNB Token
users <- bnbFiltered[,1:2]
# users
sorted_users <- users %>% filter(Seller <= Buyer)
users_to_swap <- users %>% filter(Seller > Buyer)
users_to_swap[, c(1,2)] <- users_to_swap[, c(2,1)]
sorted_users <- merge(sorted_users, users_to_swap)
# sorted_users
bs.bnb.distribution <- sorted_users %>% group_by(.dots = c("Seller", "Buyer")) %>% count() %>% ungroup
nrow(bs.bnb.distribution)

# StatusNetwork Token (sn)
users <- statusnetworkFiltered[,1:2]
# users
sorted_users <- users %>% filter(Seller <= Buyer)
users_to_swap <- users %>% filter(Seller > Buyer)
users_to_swap[, c(1,2)] <- users_to_swap[, c(2,1)]
sorted_users <- merge(sorted_users, users_to_swap)
# sorted_users
bs.statusnetwork.distribution <- sorted_users %>% group_by(.dots = c("Seller", "Buyer")) %>% count() %>% ungroup
nrow(bs.statusnetwork.distribution)

# MCAP Token
users <- mcapFiltered[,1:2]
# users
sorted_users <- users %>% filter(Seller <= Buyer)
users_to_swap <- users %>% filter(Seller > Buyer)
users_to_swap[, c(1,2)] <- users_to_swap[, c(2,1)]
sorted_users <- merge(sorted_users, users_to_swap)
# sorted_users
bs.mcap.distribution <- sorted_users %>% group_by(.dots = c("Seller", "Buyer")) %>% count() %>% ungroup
nrow(bs.mcap.distribution)
```

```{r}
# Distributions for BNB
bs.bnb.distribution %>% arrange(-n) %>% head(400)
# bs.bnb.distribution
# det_outliers <- bs.bnb.distribution %>% group_by(n) %>% summarize(count = n())

# test <- det_outliers %>% group_by(n) %>% summarize(count = n())
# test %>% arrange(-count) %>% head(400)

#
# fit <- fitdistr(det_outliers$count, densfun="normal")
# fit$estimate

# Filtering out the extreme transaction which are less than 0.5 percent
# They extend the x-axis and we plotting the values on graph won't look pretty
bs.bnb.distribution <- bs.bnb.distribution %>% filter(n > 3 & n < 300)

# fit.norm.bnb <- fitdistr(bs.bnb.distribution$n, densfun="normal")  # we assume my_data ~ Normal(?,?)
fit.norm.bnb <- fitdist(bs.bnb.distribution$n, 'norm')
fit.ln.bnb <- fitdist(bs.bnb.distribution$n, 'lnorm')
fit.gamma.bnb <- fitdist(bs.bnb.distribution$n, 'gamma', lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.nbin.bnb <- fitdist(bs.bnb.distribution$n, 'nbinom')
fit.weibull.bnb <- fitdist(bs.bnb.distribution$n, 'weibull')
fit.log.bnb <- fitdist(bs.bnb.distribution$n, 'logis')
fit.unif.bnb <- fitdist(bs.bnb.distribution$n, 'unif')


gofstat(list(fit.gamma.bnb,fit.log.bnb, fit.ln.bnb, fit.nbin.bnb, fit.norm.bnb, fit.unif.bnb, fit.weibull.bnb))

# Plot histogram
hist(bs.bnb.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

# Plot curves on the above histgram
curve(dnorm(x, fit.ln.bnb$estimate[1], fit.ln.bnb$estimate[2]), col="blue", lwd=1, add=T)
curve(dnorm(x, fit.norm.bnb$estimate[1], fit.norm.bnb$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.gamma.bnb$estimate[1], fit.gamma.bnb$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.nbin.bnb$estimate[1], fit.nbin.bnb$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.unif.bnb$estimate[1], fit.unif.bnb$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.log.bnb$estimate[1], fit.log.bnb$estimate[2]), col="brown", lwd=2, add=T)
curve(dnorm(x, fit.weibull.bnb$estimate[1], fit.weibull.bnb$estimate[2]), col="pink", lwd=2, add=T)


# Distributions for Status Network
# bs.statusnetwork.distribution %>% arrange(-n) %>% head(400)
# bs.statusnetwork.distribution

# Filtering out the extreme transaction which are less than 0.5 percent
# They extend the x-axis and we plotting the values on graph won't look pretty
bs.statusnetwork.distribution <- bs.statusnetwork.distribution %>% filter(n > 3 & n < 300)

fit.norm.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'norm')
fit.ln.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'lnorm')
fit.gamma.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'gamma', lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.nbin.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'nbinom')
fit.weibull.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'weibull')
fit.log.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'logis')
fit.unif.statusnetwork <- fitdist(bs.statusnetwork.distribution$n, 'unif')


gofstat(list(fit.gamma.statusnetwork,fit.log.statusnetwork, fit.ln.statusnetwork, fit.nbin.statusnetwork, fit.norm.statusnetwork, fit.unif.statusnetwork, fit.weibull.statusnetwork))

# Plot histogram
hist(bs.statusnetwork.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

# Plot curves on the above histgram
curve(dnorm(x, fit.ln.statusnetwork$estimate[1], fit.ln.statusnetwork$estimate[2]), col="blue", lwd=1, add=T)
curve(dnorm(x, fit.norm.statusnetwork$estimate[1], fit.norm.statusnetwork$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.gamma.statusnetwork$estimate[1], fit.gamma.statusnetwork$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.nbin.statusnetwork$estimate[1], fit.nbin.statusnetwork$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.unif.statusnetwork$estimate[1], fit.unif.statusnetwork$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.log.statusnetwork$estimate[1], fit.log.statusnetwork$estimate[2]), col="brown", lwd=2, add=T)
curve(dnorm(x, fit.weibull.statusnetwork$estimate[1], fit.weibull.statusnetwork$estimate[2]), col="pink", lwd=2, add=T)


# Distributions for MCAP
# bs.mcap.distribution %>% arrange(-n) %>% head(400)
# bs.mcap.distribution

# Filtering out the extreme transaction which are less than 0.5 percent
# They extend the x-axis and we plotting the values on graph won't look pretty
bs.mcap.distribution <- bs.mcap.distribution %>% filter(n > 3 & n < 300)

fit.norm.mcap <- fitdist(bs.mcap.distribution$n, 'norm')
fit.ln.mcap <- fitdist(bs.mcap.distribution$n, 'lnorm')
fit.gamma.mcap <- fitdist(bs.mcap.distribution$n, 'gamma', lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.nbin.mcap <- fitdist(bs.mcap.distribution$n, 'nbinom')
fit.weibull.mcap <- fitdist(bs.mcap.distribution$n, 'weibull')
fit.log.mcap <- fitdist(bs.mcap.distribution$n, 'logis')
fit.unif.mcap <- fitdist(bs.mcap.distribution$n, 'unif')


gofstat(list(fit.gamma.mcap,fit.log.mcap, fit.ln.mcap, fit.nbin.mcap, fit.norm.mcap, fit.unif.mcap, fit.weibull.mcap))

# Plot histogram
hist(bs.mcap.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

# Plot curves on the above histgram
curve(dnorm(x, fit.ln.mcap$estimate[1], fit.ln.mcap$estimate[2]), col="blue", lwd=1, add=T)
curve(dnorm(x, fit.norm.mcap$estimate[1], fit.norm.mcap$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.gamma.mcap$estimate[1], fit.gamma.mcap$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.nbin.mcap$estimate[1], fit.nbin.mcap$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.unif.mcap$estimate[1], fit.unif.mcap$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.log.mcap$estimate[1], fit.log.mcap$estimate[2]), col="brown", lwd=2, add=T)
curve(dnorm(x, fit.weibull.mcap$estimate[1], fit.weibull.mcap$estimate[2]), col="pink", lwd=2, add=T)
```

Conclusion - Curve in Blue color fits the entire distribution quite well for all three tokens. So LogNormal seems to be the best fit
```r
fit.ln.bnb
fit.ln.statusnetwork
fit.ln.mcap
```

Project Part 2
Load prices for the three tokens
```{r}
statusnetworkPrice = read.table(file="prices/statusnetwork", header=T,sep="\t")
bnbPrice = read.table(file="prices/bnb.csv", header=T,sep=",")
mcapPrice = read.table(file="prices/mcap", header=T,sep="\t")
colNames <- c("Date","Open","High","Low", "Close" ,"Volume","MarketCap")
colnames(statusnetworkPrice) <- colNames
colnames(bnbPrice) <- colNames
colnames(mcapPrice) <- colNames
# bnbPrice
# mcapPrice
# statusnetworkPrice
# bnbFiltered
# statusnetworkFiltered

colNames <- c("Seller", "Buyer", "Unixdate", "Amount")
colnames(bnbFiltered) <- colNames
colnames(statusnetworkFiltered) <- colNames
colnames(mcapFiltered) <- colNames

```

Bring dates in two dataframs into same format
```{r}
bnbPrice$Date<-as.Date(bnbPrice$Date,format="%m/%d/%Y")
bnbPrice$Date<- as.Date(as.POSIXct(bnbPrice$Date, origin="1970-01-01"))
bnbFiltered$Unixdate<- as.Date(as.POSIXct(bnbFiltered$Unixdate, origin="1970-01-01"))
# bnbFiltered

statusnetworkPrice$Date<-as.Date(statusnetworkPrice$Date,format="%m/%d/%y")
statusnetworkPrice$Date<- as.Date(as.POSIXct(statusnetworkPrice$Date, origin="1970-01-01"))
statusnetworkFiltered$Unixdate<- as.Date(as.POSIXct(statusnetworkFiltered$Unixdate, origin="1970-01-01"))
# statusnetworkPrice

mcapPrice$Date<-as.Date(mcapPrice$Date,format="%m/%d/%y")
mcapPrice$Date<- as.Date(as.POSIXct(mcapPrice$Date, origin="1970-01-01"))
mcapFiltered$Unixdate<- as.Date(as.POSIXct(mcapFiltered$Unixdate, origin="1970-01-01"))
# mcapFiltered
```

Build Regression Models for three tokens
```{r}
# BNB buys freq distribution
buys.distribution.bnb  <- bnbFiltered %>% group_by(Buyer) %>% summarise(n = n()) %>% ungroup
colnames(buys.distribution.bnb) <- c("Buyer","Frequency")
sortedBNB_Buyer <- buys.distribution.bnb[order(-buys.distribution.bnb$Frequency),]

# Most active buyer and total count of transaction that they made
head(sortedBNB_Buyer, 1)

# BNB sells freq distribution
sells.distribution.bnb  <- bnbFiltered %>% group_by(Seller) %>% summarise(n = n()) %>% ungroup
colnames(sells.distribution.bnb) <- c("Seller","Frequency")
sortedBNB_Seller <- sells.distribution.bnb[order(-sells.distribution.bnb$Frequency),]

# Most active seller and total count of transaction that they made
head(sortedBNB_Seller, 1)

# Regression
bnbRegression <- merge(bnbFiltered, bnbPrice, by.x="Unixdate", by.y="Date")

lm.fit.bnb = lm(Low ~ Amount + Open, data= bnbRegression)
summary(lm.fit.bnb)

plot(lm.fit.bnb)


# Status Network buys freq distribution
buys.distribution.statusnetwork  <- statusnetworkFiltered %>% group_by(Buyer) %>% summarise(n = n()) %>% ungroup
colnames(buys.distribution.statusnetwork) <- c("Buyer","Frequency")
sortedStatusNetwork_Buyer <- buys.distribution.statusnetwork[order(-buys.distribution.statusnetwork$Frequency),]

# Most active buyer and total count of transaction that they made
head(sortedStatusNetwork_Buyer, 1)

# BNB sells freq distribution
sells.distribution.statusnetwork  <- statusnetworkFiltered %>% group_by(Seller) %>% summarise(n = n()) %>% ungroup
colnames(sells.distribution.statusnetwork) <- c("Seller","Frequency")
sortedStatusNetwork_Seller <- sells.distribution.statusnetwork[order(-sells.distribution.statusnetwork$Frequency),]

# Most active seller and total count of transaction that they made
head(sortedStatusNetwork_Seller, 1)

# Regression
statusnetworkRegression <- merge(statusnetworkFiltered, statusnetworkPrice, by.x="Unixdate", by.y="Date")

lm.fit.statusnetwork = lm(Low ~ Amount + Open, data= statusnetworkRegression)
summary(lm.fit.statusnetwork)

plot(lm.fit.statusnetwork)


# MCAP buys freq distribution
buys.distribution.mcap  <- mcapFiltered %>% group_by(Buyer) %>% summarise(n = n()) %>% ungroup
colnames(buys.distribution.mcap) <- c("Buyer","Frequency")
sortedStatusNetwork_Buyer <- buys.distribution.mcap[order(-buys.distribution.mcap$Frequency),]

# Most active buyer and total count of transaction that they made
head(sortedStatusNetwork_Buyer, 1)

# MCAP sells freq distribution
sells.distribution.mcap  <- mcapFiltered %>% group_by(Seller) %>% summarise(n = n()) %>% ungroup
colnames(sells.distribution.mcap) <- c("Seller","Frequency")
sortedStatusNetwork_Seller <- sells.distribution.mcap[order(-sells.distribution.mcap$Frequency),]

# Most active seller and total count of transaction that they made
head(sortedStatusNetwork_Seller, 1)

# Regression
mcapRegression <- merge(mcapFiltered, mcapPrice, by.x="Unixdate", by.y="Date")

lm.fit.mcap = lm(Low ~ Amount + Open, data= mcapRegression)
summary(lm.fit.mcap)

plot(lm.fit.mcap)

```
